Escaping RGBland: Selecting Colors for Statistical Graphics

### 2007-11-08 pkg/paper/Palettes/CSDA.Rnw
fiddle pie chart
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@30 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=\textwidth}
\begin{figure}[b!]
\begin{center}
<<wheel, fig=TRUE, height=4, width=11>>=
par(mar = rep(0.8, 4), mfrow = c(1, 2))
par(mfrow = c(1,2), mar = c(1,1,1,1), oma = c(0,0,0,0))
par(lwd=3)
pie(rep(1,6), radius = 1, col = rainbow(6), labels = 360 * 0:5/6)
par(lwd=0.5, new=TRUE)
pie(rep(1, 100), radius = 1, col = rainbow(100), border = NA, labels = NA)
par(lwd=3)
pie(rep(1,6), radius = 1, col = rainbow_hcl(6, c = 50, l = 70), 
    labels = 360 * 0:5/6)
par(lwd=0.5, new=TRUE)
pie(rep(1, 100), radius = 1, col = rainbow_hcl(100, c = 50, l = 70), border = NA, labels = NA)
@
\caption{\label{fig:wheel} HSV-based and HCL-based color wheel.}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=\textwidth}
\begin{figure}[b!]
\begin{center}
<<wheel, fig=TRUE, height=4, width=11>>=
par(mar = rep(0.8, 4), mfrow = c(1, 2))
par(mfrow = c(1,2), mar = c(1,1,1,1), oma = c(0,0,0,0))
par(lwd=3)
pie(rep(1,6), radius = 1, col = rainbow(6), labels = 360 * 0:5/6)
par(lwd=0.5, new=TRUE)
pie(rep(1, 100), radius = 1, col = rainbow(100), border = NA, labels = NA)
par(lwd=3, new=TRUE)
pie(1, radius=0.5, labels=NA)
par(lwd=0.5, new=TRUE)
pie(1, radius=0.5, border=NA, labels=NA)
par(lwd=3)
pie(rep(1,6), radius = 1, col = rainbow_hcl(6, c = 50, l = 70), 
    labels = 360 * 0:5/6)
par(lwd=0.5, new=TRUE)
pie(rep(1, 100), radius = 1, col = rainbow_hcl(100, c = 50, l = 70), border = NA, labels = NA)
par(lwd=3, new=TRUE)
pie(1, radius=0.5, labels=NA)
par(lwd=0.5, new=TRUE)
pie(1, radius=0.5, border=NA, labels=NA)
@
\caption{\label{fig:wheel} HSV-based and HCL-based color wheel.}
\end{center}
\end{figure}
